Comparison to Christensen et al. 2018

### 2019-02-12 doc/paper-comparison.Rmd
Make a trivial change to trigger a Travis build

Side-by-side comparison of LDATS results with analysis from Christensen et al 2018.

@@

| Step | Changes from Christensen et al 2018 to `LDATS` | Effect on comparison | Recommendations for future users |
|:---------------|:------------------------|:-----------------------|:----------------------------|
|Data|Paper adjusts abundances according to unit effort, while `LDATS` uses raw capture numbers.|None: run comparison using adjusted data|Use raw, unweighted abundances.|
|LDA model selection|Paper conservatively overestimated the number of parameters for calculating AIC for model selection. `LDATS` calculates AIC appropriately.|Paper LDA selects 4 topics, while `LDATS` finds 6. Compare all combinations of paper and `LDATS` LDA models and changepoint models| Use `LDATS` AIC calculation.|
|Changepoint model document weights|Paper weighted all sampling periods equally regardless of abundance. `LDATS` by default weights the information from each sampling period according to the number of individuals captured (i.e. the amount of information gleaned about the underlying community composition).|None; use `weights = NULL` to set all weights equal to 1 for LDATS| Weight sampling periods according to abundance|
|Overall LDA + changepoint results| All combinations of LDA + changepoint model find 4 changepoints at approximately the same time steps|Choice of LDA model has more of an effect than choice of changepoint model|`LDATS` reflects best practices, but the paper methods produced qualitatively similar results.|

>>>>

This document prodives a side-by-side comparison of LDATS (v0.1.0) results with analysis from [Christensen et al. 2018](https://esajournals.onlinelibrary.wiley.com/doi/full/10.1002/ecy.2373).

@@

| Step | Changes from Christensen et al 2018 to `LDATS` | Effect on comparison | Recommendations for future users |
|:---------------|:------------------------|:-----------------------|:----------------------------|
|Data|Paper adjusts abundances according to unit effort, while `LDATS` uses raw capture numbers.|None: run comparison using adjusted data|Use raw, unweighted abundances.|
|LDA model selection|Paper conservatively overestimated the number of parameters for calculating AIC for model selection. `LDATS` calculates AIC appropriately.|Paper LDA selects 4 topics, while `LDATS` finds 6. Compare all combinations of paper and `LDATS` LDA models and changepoint models| Use `LDATS` AIC calculation.|
|Changepoint model document weights|Paper weighted all sampling periods equally regardless of abundance. `LDATS` by default weights the information from each sampling period according to the number of individuals captured (i.e. the amount of information gleaned about the underlying community composition).|None; use `weights = NULL` to set all weights equal to 1 for LDATS| Weight sampling periods according to abundance|
|Overall LDA + changepoint results| All combinations of LDA + changepoint model find 4 changepoints at approximately the same time steps|Choice of LDA model has more of an effect than choice of changepoint model|`LDATS` reflects best practices, but the paper methods will produce qualitatively similar results.|
